Weed and Corn segmentation through Convolutional Neuronal Networks

### 2017-07-06 PaperBCJ.tex
modifaciones
06-julio

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}
\usepackage{graphicx}
\usepackage{array}
\usepackage{filecontents}
\usepackage{caption}
\usepackage[noadjust]{cite}
\captionsetup[table]{position=bottom}   %% or below

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Precise Weed and Maize classification through Convolutional Neuronal Networks }

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
Deep Learning has played a very important role in modern times, being very used in Artificial Vision and especially in Pattern Recognition, which opens many doors in the fields of application among which is precision agriculture. In this paper we present the study of a convolutional neural network with two classes applied to the classification of plants of maize and weeds in real time, focused to fields of maize in its initial stage. The algorithm has two stages, segmentation of images and classification.  In the segmentation we wanted to separate the target plant from the original image. While the classification is possible through a convolutional neural network, previously trained with a dataset generated through the segmentation stage. The performance of the network is illustrated by analysis and comparisons with different network architectures, then with the network that presented better results in training, we experimented by modifying its number of filters, to analyze their  behavior. Finally, the resulting network was tested on different processors to compare classification times.\\
\end{abstract}

@@

\section{Introduction}
During the last centuries, huge progress has taken place in science and technology developments. Significant milestones such as Communications, Numerical Computer Control and the miniaturization of components have benefited social and industrial sectors on its approach to solve specific problems. 
\\

Globalization has permitted countries who are not leader technology developers, like Ecuador, to receive bleeding edge technological products in order to satisfy requirements and propose solutions to still-unresolved problems.
\\

Industry transformation is a science evolution example; manufacturing, food, and information industries, among others, are signs of this industrial revolution. However there are fields still unexplored  in Ecuador like agroindustry. Agriculture in Ecuador has not changed much since precolombine times; while it is true that there are efficient agriculture practices, the lack of technological resources make it impossible for the country to exploit its true potential as an agricultural producer.
\\

Nowadays, one of agriculture challenges is the development of precision agriculture techniques focused on Weed and Crop segmentation. There are studies that show the impact of Weed in corn crops \cite{suarez2005distintos}; its yield is affected by 5000 kg/ha. Currently, growing development of Artificial Vision and Machine Learning algorithms allow researchers to propose solutions for Weed Segmentation in Crops. 
\\

One of the first approximations to the algorithms of detection of Crops was  developed in 1996 \cite{brivot1996segmentation}, this algorithm permitted to segment crops from weed, it could be possible by the use of IR Images, the image is processed by a hysteresis umbral and the method of Min Neighbouring to identify the row of crops. In recent years the implementation of Machine Learning has opened new possibilities for differentiate the Weed from the crops, recently \cite{cheng2015feature} there had been developed an algorithm by the use of Harris Corner detector, Feature Detector and using the DBSCAN (Density-based spartial clustering of apllications with noise) , it demonstrates an effectiveness of  98\% in the identification of Weeds in the Rice, Araguez \textit{et. al} \cite{equipo2006proceedings}  performed their segmentation through the analysis of the green hystogram and performing the segmentation of the crop and weed by classifiers not specified in the document. 
\\

Hong and Lei \cite{jeon2011robust} developed their approximation by using an optimal method for detection in various types of luminosity, they achived this by the use an ANN for weed and maize classification, with a precision of 92.5\%,  also there had been developed an algorithm \cite{hlaing2014weed}, that through binarization methods of OTSU and Watershed for the segmentation of the images. While its classification was given through an areas analysis to perform a thresholding, although the method is computationally effective when the Weed distribution does not resemble the size to the crop plant, its error increases when there is more density of crop than of weed. Romeo \textit{et. al} \cite{romeo2012crop} propose to use a fuzzy clustering approach to correctly segment the crop green.
\\

The segmentation of weed and crops is not closed to color images, using a multispectral camera  \cite{potena2016fast} permitted to obtain RGB and NIR images, for the segmentation and classification, then the images used a light CNN for the first process and a Deep CNN for classification in Crops, its accuracy is up to 98\% in the identification of weeds. One of the most dificults things for the identification of crops is the generation of Datasets due to presence of Weed in the images of training, but there could be correctly generated by a Convolutional Neural Network \cite{di2016automatic} achieving a acceptable accuracy for the generation of Datasets. 
\\

\section{Matherials and Methods}
The development of the model for the weed and maize detection algorithm using convolutional neural networks is described below.
\\
\subsection{Hardware}
For the training and image capturing stages, the following elements were used: a Raspberry Pi 3 with Pi Camera V2.1 for image acquisition, it was configured to obtain a video at a resolution of 1280x720 pixels in order to get more detail in the segmented images. Due to the popularity of the GPU computing, it was neccesary to consider hardware compatible with Parallel Computing like the Graphic Cards manufactured by NVIDIA, they have the advantage of better times of processing compared to CPU, in order to optimize the time of image processing and training of Deep Learning Models, so we used a Computer with a Nvidia Graphics Card GTX950M. Also it was neccesary to consider the use of a CPU Core i7 2.7 Ghz, 8 cores and the CPU of the Raspberry Pi 3, a ARM Cortex-A53, 1.2GHz, 4 cores for testing the classification of images of the Network.   
\\

@@

For the application in this documents it requires the use of powerful libraries of Image Processing and Deep Learning Development, we considered to use Open Software for extend its use in future prototypes, due to this considerations we had chosen the OpenCV library for its computational efficiency and focus on real-time application \cite{opencv_library} in this  case, it was used for acquisition and segmentation of the sample images. Also we had considered Caffe because it is intended to use in training and developing general-purpose Convolutionals Neural Networks and other Deep Lerning models \cite{jia2014caffe} with fully support of CUDA GPU Computation and a generous database of resources for learning,	
\\

@@

\subsection{Dataset Description}
Due to the lack of datasets of Weed and Maize plants, it was neccesary to search crops of maize in its initial stage, for that purpose we had traslated to P\'illaro, it is a city located in the Tungurahua Province on the center of the Ecuadorian Highlands region, P\'illaro is recognized producer of Andean Crops such as: Maize, Potatoes and Fruits so here we could find many crops of Maize useful for our purpose. \\

Samples were obtained from images captured in those maize fields , we considered to choose maize crops where we could visually discriminate the plants of the crop and the weed. Maize in stages V3-V7(3-7 leafs) \cite{fassio1998maiz} were used to take samples. To record the samples we centered the camera over the target plant, insuring that the capture shows all features of the maize plant, it was possible by monitoring the get of samples by an external display. An examples of the images captured are shown below.

@@

Also it was neccesary  to obtain images of the most common weed plants of the maize crops in Pillaro, to allow the Network to discriminate both classes of the Dataset. \\

Then, through a digital image processing, the images were segmented to differentiate them from the soil and other non-plant elements, then the images were masked to provide the dataset features of color of the Maize and Weed. Once the segmented images were obtained, they were removed those that had a resolution lower than 64x64 pixels, because it's smaller than size of input layer of the network, besides it was not convenient its processing since its total area was much smaller than the samples of corn, which is the purpose of this document, later, the images were saved in a png format. The process described before, was illustrated in the next figure. \\
	\begin{figure}[h]
	\centering
	\includegraphics[width=3.2in]{procesamiento}
	\caption{Preprocessing to obtain samples for the dataset}
	\label{fig_sim}
	\end{figure}

To highlight we had labelled the samples manually in two classes. In the following image we present the final results of the processed images that conform the dataset.\\

@@

Once we completed the processing of the images, it were obtained 2835 images of Maize and 880 images of Weed, Lee \textit{et. al} \cite{lee2015deep} said that once CNN has reached an acceptable accuracy, the dataset could extend by Geometric Transformations, in addition \cite{sladojevic2016deep}  they mention that this allows to reduce the overfitting and to improve the precision in the training, reason why we made 11 rotations each 30 degrees, obtaining in this way to increase the dataset in 12 times and have better chances of recognizing plants that are in any orientation. \\

@@

\begin{table}[h!]
\centering
\begin{tabular}{| c | c | c | c | c |} 
 \hline
 Phase & Train & Validation & Test & Total \\ [1ex] 
 \hline
 Maize & 25695 & 8325 & 200 & 34220  \\ 
 Weed & 8560 & 2000 & 200 & 10760\\ 
 \hline
\end{tabular}
\caption{Distribution of the Dataset of each class}
\label{table:1}
\end{table}

\subsection{Convolutional Neuronal Network}
	After the last step have been terminated, it is neccesary classify the images of Maize and Weed, a high accurate method of Image Classification is Convolutional Neuronal Networks(CNN), those models are complex but efficient with a highly rate of discrimination and its demostrated that they have good results in Image Classification, Object Detection and Fine-Grained  Classification \cite{sharif2014cnn}. Their are also applied in Precision Agriculture \cite{potena2016fast} for the correct identification of plants.
\\

One of the characteristics of the CNN is that they can have multiple architectures, each architecture can reach different result depending of the application , for the present document we have considered four CNN architectures: Two models were chose of the Caffe Zoo Model(it's a free resource provided by Caffe Developers), LeNet and AlexNet also Potena and Nardi had used two additional types of Models, sNET and cNET, they were sucessfully proved in identification of plants in crops\cite{potena2016fast}, with the Nets chosen, each one was trained with a same Solver of type AdaDelta and with the same dataset, the results of training are the following. \\
\begin{table}[h!]
\centering
\begin{tabular}{|l c c c c|} 
 \hline
 Parameters & LeNet & AlexNet & cNET & sNET \\ [0.75ex] 
 \hline
 Input size of images & 32x32 & 64x64 & 64x64 & 64x64 \\ 
 Layers numbers & 9 & 11 & 8 & 4\\
 Number of parameters & 652500 & 20166688 & 6421568 & 135872 \\ 
 Iterations & 3000 & 3000 & 4500 & 3000 \\ 
  Accuracy(\%) & 78.84 & 95.266 & 99.33 & 90.4 \\
  Loss(\%) & 44.8471 & 12.7256 & 5.86 & 781.3 \\ [1ex] 
 \hline 
\end{tabular}
\caption{Distribution of the Dataset of each class}
\label{table:2}
\end{table}

Inside of the shown parameters in the Table {table:2}, we considered the net who achieved the highest rate of accuracy and lowest rate of loss, clearly the cNET is the chosen due it shows a precission equal to human classification. The following picture shows the process of training of the cNET \\
Inside of the shown parameters in the Table \ref{table:2}, we considered the net who achieved the highest rate of accuracy and lowest rate of loss, clearly the cNET is the chosen due it shows a precission equal to human classification. The following picture shows the process of training of the cNET. \\

	\begin{figure*}[htb]
	\centering
	\includegraphics[width=6.5 in]{arquitectura}
	\caption{ The schematic of CNet }
	\label{fig_sim}
	\end{figure*}

	\begin{figure}[h]
	\centering
	\includegraphics[width=2.3in]{entrenamiento}
	\caption{ Graph of the Training Process }
	\label{fig_sim}
	\end{figure}

Although results given for the net are excellents, one of the main purposes of this paper is the implementation in real time, so the number of parameters to be computed must be a problem, so we considered to modify the net in order to improve the processing time. To achive this, it was neccesary to reduce the number of filters from 64 to 16, this permitted to reduce the number of parameters to 1651376(it's a 25\% of parameters than the original net), and what about the precision of the net, it was slighty affected but it reach a 97.2\% of accuracy, the results of the processing will be explained with more detail in the next section.

	\section{Test}

For this stage, we considered an extra dataset with 200 images of maize plants and 203 images of weed, the results were comparated between cNET with 64 and 16 filters, each one would be  
\begin{table}[h!]
\centering
\begin{tabular}{|l|c|c|p{2cm}|}  
 \hline
 \multicolumn{4}{ |c| }{GPU} \\
 \hline
   cNET & \% Accuracy Weed & \% Accuracy Maize  & Average time of classification   \\ 
 \hline 
 64 Filters & 81.6 & 88.36 & 2.34 ms  \\ [0.75ex]
 \hline
 16 Filters & 85.71 & 87.13 & 951  $\mu$ s \\ [0.75ex]
  \hline
 \multicolumn{4}{ |c| }{CPU} \\
 \hline
   & \% Accuracy Weed & \%Accuracy Maize  & Average time of classification \\ 
 \hline 
 64 Filters & 81.6 & 88.36 & 51.6 ms  \\ [0.75ex]
 \hline
 16 Filters & 85.71 & 87.13 & 17.23 ms \\ [0.75ex]
  \hline
 \multicolumn{4}{ |c| }{CPU Raspberry Pi 3} \\
 \hline
   & \% Accuracy Weed & \%Accuracy Maize  & Average time of classification\\ 
 \hline 
 64 Filters & 81.6 & 88.36 & 615 ms  \\ [0.75ex]
 \hline
 16 Filters & 85.71 & 87.13 & 161 s \\ [0.75ex]
  \hline
\end{tabular}
\caption{Test}
\label{table:2}
\end{table}

@@

\section{Conclusion}

In this paper we have studied the application of Convolutional Neuronal Networks for Classification between Maize and Weed Plants, for that we have used some CNN Architectures, the Network with best results in precision was cNET, with a 99.33 \% of accuracy of training, using a dataset of both classes  of 44580 segmented images. \\

In order to search a right processing to work in real time, we have experimented to reduce the number of filters of the Layers of the Net from 64 to 16 filters, achiveiving to reduce the number of parameters to be computed during the classification , we obteined a classification time 2.5 times less than the original Net of 64 filters , this change had a small impact in the training accuray of the net, it value fell 1 \% in comparation with the original net. \\

Also, by using different methods to classify the images in our experiments, the results showed that the best time of classification was achieved by using a Nvidia Graphic Cards, this is due the Parallel Architecture that this GPU has and also it has fully support for the computation platform CUDA, it demostrated to be 18 times faster than a normal CPU and 170 times faster than a Raspberry Pi 3. \\

The study demostrated that is better to perform some geometrical tranformations to the Dataset images due it benefits to improve the  classification of plants because the plants ever have different orientations in the crop field.

@@

The authors would like to thank to the "Granja Agroecol\'ogica y Demostrativa" of P\'illaro City and owners of corn crops of the city which allowed us to take samples of plants, to obtain to conform the dataset of the project. \\

This work has been supported by the University of the Army "ESPE"  Latacunga.

@@

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)

\bibliographystyle{IEEEtran}
\bibliography{bibliografiapaper}

>>>>

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}
\usepackage{graphicx}

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Weed and Corn segmentation through Convolutional Neuronal Networks }

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
Today the computation stays i 
\end{abstract}

@@

\section{Introduction}
% no \IEEEPARstart

% You must have at least 2 lines in the paragraph with the drop letter
% (should never be an issue)
I wish you the best of success.

\hfill mds

\hfill August 26, 2015

\subsection{Subsection Heading Here}
Subsection text here.

\subsubsection{Subsubsection Heading Here}
Subsubsection text here.

\section{Introduction}
During the last centuries, significant progress has taken place in science and technology developments. Significant milestones in diverse areas such as communications, numerical computer control and the miniaturization of components have benefited industrial sectors, providing new means to approach problems differently. 
\\

The availability of leading edge technologies  has considerably increased, thus becoming more accessible to people. This effect of globalization has allowed many countries to have access to state-of-the-art technological products, promoting its application in different areas to generate alternative and more efficient solutions to conventional problems.

\\

Technological advances have caused industry transformations; manufacturing, food processing, and information industries among others, have gone through dramatic changes with industrial revolution. However there are fields that have not been significantly influenced by technological development in Ecuador, as it is the case of agroindustry. Agriculture in Ecuador has undergone some changes since colonial times; while it is true that there are efficient agricultural practices, the lack of technological resources make it impossible for the country to exploit its true potential as an agricultural producer. Also, the excessive use of pesticides have a negative effect on the production, soil, and water quality. 
\\

Nowadays, one of agriculture challenges is the development of precision agriculture techniques focused on Weed and Crop segmentation. There are studies that show the impact of Weed in corn crops \cite{Suarez:Pinero}; its yield is affected by 5000 kg/ha. Currently, growing development of Artificial Vision and Machine Learning algorithms allow researchers to propose solutions for Weed Segmentation in Crops. 
\\

One of the first approximations to the algorithms of detection of Crops was  developed in 1996\cite{Brivot:Marchant}, this algorithm permitted to segment crops from weed, it could be possible by the use of IR Images, the image is processed by a hysteresis umbral and the method of Min Neighbouring to identify the row of crops. In recent years the implementation of Machine Learning has opened new possibilities for differentiate the Weed from the crops, recently \cite{Cheng:Mason} there had been developed an algorithm by the use of Harris Corner detector, Feature Detector and using the DBSCAN (Density-based spartial clustering of apllications with noise) , it demonstrates an effectiveness of  98\% in the identification of Weeds in the Rice, Araguez \textit{et. al} \cite{Araguez}  performed their segmentation through the analysis of the green hystogram and performing the segmentation of the crop and weed by classifiers not specified in the document. 
\\

Hong and Lei \cite{Hong:Lei} developed their approximation by using an optimal method for detection in various types of luminosity, they achived this by the use an ANN for weed and maize classification, with a precision of 92.5\%,  also there had been developed \cite{Su:Hnin} through binarization methods of OTSU and Watershed for the segmentation of the images, while the classification was given through a areas analysis to perform a thresholding, although the method is computationally effective when the Weed distribution does not resemble the size to the crop plant, its error increases when there is more density of crop than of weed. Romeo \textit{et. al} \cite{Romeo} propose to use a fuzzy clustering approach to correctly segment the crop green and the same algorithm to classify the soil crop.
\\

The segmentation of weed and crops is not closed to color images, using a multispectral camera  \cite{Potena:Nardi} permitted to obtain RGB and NIR images, for the segmentation and classification, then the images used a light CNN for the first process and a Deep CNN for classification in Crops, its accuracy is up to 98\% in the identification of weeds. One of the most dificults things for the identification of crops is the generation of Datasets due to presence of Weed in the images of training, but there could be correctly generated by a Convolutional Neural Network \cite{Cicco:Potena} achieving a acceptable accuracy for the generation of Datasets 
\\

\section{Matherials and Methods}
The development of the model for the weed and maize detection algorithm using convolutional neural networks is described below.
\\
\subsection{Hardware}
For the training and image capturing stages, the following elements were used: a Raspberry Pi 3 with Pi Camera V2.1 for image recording, it was configured to obtain a video at a resolution of 640x480 pixels in order to improve the performance of image processing. Due to the popularity of the GPU computing, it was neccesary to consider hardware compatible with Parallel Computing like the Graphic Cards manufactured by NVIDIA, they have the advantage of better times of processing compared to CPU, in order to optimize the time of image processing and training of Deep Learning Models, so we used a Computer with a Nvidia Graphics Card GTX950M.
\\

@@

For the application in this documents requires the use of powerful libraries of Image Processing and Deep Learning Development, we considered to use Open Software for extend its use  in future prototypes, due to this considerations we had chosen the OpenCV library for its computational efficiency and focus on real-time application \cite{OpenCV} in this  case, it was used for acquisition and segmentation of the sample images. Also we had considered Caffe because it is intended to use in training and developing general-purpose Convolutionals Neural Networks and other Deep Lerning models \cite{caffe} with fully support of CUDA GPU Computation and a generous database of resources for learning,	
\\

@@

\subsection{Dataset Description}
Due to the lack of datasets of Weed and Maize plants, it was neccesary to search crops of maize in its initial stage, for that purpose we had traslated to P\'illaro, it is a city located in the Tungurahua Province on the center of the  the Ecuadorian Highlands region, P\'illaro is recognized producer of Andean Crops such as: Maize, Potatoes and Fruits so here we could find many crops of Maize useful for our purpose. \\

Samples were obtained from images captured in those maize fields , we considered to choose maize crops where we could visually discriminate the plants of the crop and the weed. Maize in stages V3-V7(3-7 leafs) \cite{Fassio} were used to take samples. To record the samples we centered the camera insuring that the capture shows all features of the maize plant, it was possible by monitoring the get of samples by an external display. An examples of the images captured are shown below. 
\\

@@

Then, through a digital image processing, the images were segmented to differentiate them from the soil and other non-plant elements, then the images were masked to provide the dataset features of color of the Maize and Weed. Once the segmented images were obtained, they were removed those that had a resolution lower than 64x64 pixels, because it's smaller than size of input layer of the network, besides it was not convenient its processing since its total area was much smaller than the samples of corn, which is the purpose of this document. To highlight we had labelled the samples manually in two classes. In the following image we present the final results of the processed images that conform the dataset.

@@

Once we completed the processing of the images were obtained 2369 images of Maize and 632 images of Weed, \textbf{Seng} \cite{SengChang} said that once CNN has reached an acceptable accuracy, the dataset could extend by Geometric Transformations, because we will develop a  system  for classify the maize in any position , we considered to rotate the source sample to 90º,180º and 270º so the dataset will be treble, improving the accuracy of the model. \\

@@

\begin{table}[h!]
\centering
\begin{tabular}{|c | c | c | c | c|} 
 \hline
 Phase & Train & Validation & Test & Total \\ [0.5ex] 
 \hline
 Maize & 7581 & 1895 & 787 & 9476 \\ 
 Weed & 2023 & 505 & 300 & 2528\\[1ex] 
 \hline 
\end{tabular}
\caption{Distribution of the Dataset of each class}
\label{table:1}
\end{table}

\subsection{Convolutional Neuronal Network}
	After the last step have been terminated, it is neccesary classify the images of Maize and Weed, a high accurate method of Image Classification is Convolutional Neuronal Networks(CNN), those models are complex but efficient with a highly rate of discrimination and its demostrated that they have good results in Image Classification, Object Detection and Fine-Grained  Classification \cite{Razavian}. Their are also applied in Precision Agriculture \cite{Potena:Nardi} for the correct identification of plants.
\\

One of the characteristics of the CNN is that they can have multiple architectures, each architecture can reach different result depending of the application , for the present document we have considered four CNN architectures: Two models were chose of the Caffe Zoo Model(it's a free resource provided by Caffe Developers), LeNet and AlexNet also Potena and Nardi had used two additional types of Models, sNET and cNET, they were sucessfully proved in identification of plants in crops\cite{Potena:Nardi}, with the Nets chosen, each one was trained with a same Solver of type AdaDelta and with the same dataset, the results of training are the following. 
\\
\begin{table}[h!]
\centering
\begin{tabular}{|l c c c c|} 
 \hline
 Parameters & LeNet & AlexNet & cNET & sNET \\ [0.5ex] 
 \hline
 Input size of images & 32x32 & 64x64 & 64x64 & 64x64 \\ 
 Layers numbers & 9 & 11 & 8 & 4\\
 Number of parameters & 652500 & 20166688 & 6421568 & 135872 \\ 
 Iterations & 3000 & 3000 & 4500 & 3000 \\ 
  Accuracy(\%) & 78.84 & 95.266 & 99.33 & 90.4 \\
  Loss(\%) & 44.8471 & 12.7256 & 5.86 & 781.3 \\ [1ex] 
 \hline \\
\end{tabular}
\caption{Distribution of the Dataset of each class}
\label{table:1}
\end{table}

Inside of the shown parameters in the Table {table:1}, we considered the net who achieved the highest rate of accuracy and lowest rate of loss, clearly the cNET is the chosen due it shows a precission equal to human classification. The following picture shows the process of training of the cNET \\

	\begin{figure}[h]
	\centering
	\includegraphics[width=3.2in]{entrenamiento}
	\caption{ Graph of the Training Process }
	\label{fig_sim}
	\end{figure}

	\section{Test}
	%Codigo para la Implementacion del Algoritmo

@@

\section{Conclusion}
The conclusion goes here.

@@

The authors would like to thank...

@@

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
\begin{thebibliography}{1}

\bibitem{Suarez:Pinero}
R. ~Su\'arez, J. ~Pi\~neiro and J. ~Valladares \emph{Distintos Sistemas De Escarda En Ma\'iz Forrajero} . Vol ~II. \hskip 1em plus
  0.5em minus 0.4em\relax Gij\'on , Spain: Publicaciones SERIDA, 2005. Web. 3 Mar. 2017.

\bibitem{Brivot:Marchant}
R.~Brivot and J.~A. Marchant, \emph{Segmentation of plants and weeds for a precision crop protection robot using infrared images} Vol ~143 Issue 2 \hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: IEE Proceedings - Vision, Image and Signal Processing, 1996.

  \bibitem{Cheng:Mason}
B.~Cheng and E.T. ~Matson, \emph{A Feature-Based Machine Learning Agent for Automatic Rice and Weed Discrimination} Artificial Intelligence and Soft Computing: 14th International Conference, ICAISC 2015 Part II \hskip 1em plus
  0.5em minus 0.4em\relax Zakopane, Poland , 2015.

  \bibitem{Hong:Lei}
~Hong. Y. Jeon, ~Lei F. Tian  and ~Heping Zhu, \emph{Robust Crop and Weed Segmentation under Uncontrolled Outdoor Ilumination} Vol ~143 Issue 2 \hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: IEE Proceedings - Vision, Image and Signal Processing, 2011.

  \bibitem{Araguez}
D.~Abad\'ia, R. Aragu\'es, A. ~Cirujeda, R. ~del Hoyo, J. ~Paniagua, T. ~Seco, V. ~Urdanoz, F. ~Us\'on and C. ~Zaragoza , \emph{SAAPIN: Un robot para el desherbado de cultivos y valoraci\'on de salinidad del suelo} Vol ~143 Issue 2 \hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: IEE Proceedings - Vision, Image and Signal Processing, 206.

 \bibitem{Su:Hnin}
R.~Cheng and J.~A. Mason, \emph{Segmentation of plants and weeds for a precision crop protection robot using infrared images} Vol ~143 Issue 2 \hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: IEE Proceedings - Vision, Image and Signal Processing, 1996.

%Revisar la extension de los nombres  
 \bibitem{Romeo}
J.~Romeo, G. ~Pajares M. ~Montalvo, J.M. ~Guerrero, M. ~Guijarro, and A. ~Ribeiro, \emph{Crop Row Detection in Maize fields Inspired on the Human VIsual Perception} Vol ~143 Issue 2 \hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: IEE Proceedings - Vision, Image and Signal Processing, 2012.

%Poner Bibliografia Correcta, Revisar	 si es neceario poner cuatro nombres
 \bibitem{Potena:Nardi}
 C.~Potena,  D.~Nardi and A. ~Pretto \emph{Fast and Accurate Crop and Weed Identification with Summarized Train Sets for Precision Agriculture} Vol ~143 Issue 2 \hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: IEE Proceedings - Vision, Image and Signal Processing, 1996.

%Poner Bibliografia Correcta, Revisar si es neceario poner cuatro nombres  
 \bibitem{Cicco:Potena}
 M.~Di Cicco, C. ~Potena, G. ~Grisetti and A.~Pretto, \emph{Automatic Model  Based Dataset Generation for Fast and Accurate Crop and Weeds Detecion} Vol ~143 Issue 2 \hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: IEE Proceedings - Vision, Image and Signal Processing, 2017.

 \bibitem{Razavian}
 A. S. ~Razavian, C. ~Potena, G. ~Grisetti and A.~Pretto, \emph{CNN Features off-the-shelf: an Astounding Baseline for Recognition} Vol ~143 Issue 2 \hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: IEE Proceedings - Vision, Image and Signal Processing, 2017.

   \bibitem{OpenCV}
 A. S. ~Razavian, C. ~Potena, G. ~Grisetti and A.~Pretto, \emph{CNN Features off-the-shelf: an Astounding Baseline for Recognition} Vol ~143 Issue 2 \hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: IEE Proceedings - Vision, Image and Signal Processing, 2017.

     \bibitem{caffe}
Jia, Yangqing and Shelhamer, Evan and Donahue, Jeff and Karayev, Sergey and Long, Jonathan and Girshick, Ross and Guadarrama, Sergio and Darrell, Trevor, \emph{Caffe: Convolutional Architecture for Fast Feature Embedding} Vol ~143 Issue 2 \hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: IEE Proceedings - Vision, Image and Signal Processing, 2014.

       \bibitem{SengChang}
Seng Chang \emph{Caffe: Convolutional Architecture for Fast Feature Embedding} Vol ~143 Issue 2 \hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: IEE Proceedings - Vision, Image and Signal Processing, 2014.

       \bibitem{Fassio}
Fassio, A., Carriquiry, A., Tojo, C. and Romero, R  \emph{MAIZ: Aspectos sobre fenolog\'ia}  \hskip 1em plus
  0.5em minus 0.4em\relax Montevideo, Uruguay:Seria T\'ecnica Nº 101, 1998.

\bibitem{IEEEhowto:kopka}
H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.

\end{thebibliography}
